「赴尘杯」2025 年普通高中学业水平选择性考试适应性演练

### 2025-01-19 Dustbound/English/Dustbound_English_I/paper.tex
fix: fill some contents
fix: :bug: 修复了中文引号在 LaTeX 中渲染的问题

The only way to prevent anyone with physical access from disabling Secure Boot is to protect the firmware settings with a password. Most UEFI firmwares provide such a feature, usually listed under the "Security" section in the firmware settings.

@@

\begin{choices}
\item Recent iterations of Xiaomi laptops give users access to the configuration of Secure Boot within the firmware only if the administrator password remains active after setting up. Users can possibly set the password in the "Security" section in the firmware settings.

@@

  \textbf{DO NOT} copy the \texttt{noPK.auth} file to the EFI system partition (ESP) of your PC! If you do this, and someone e.g. steals your PC, this person can delete the personal Platform Key in the UEFI Secure Boot firmware again, turn on "Setup Mode" on your PC again and replace your Secure Boot Keys (PK, KEK, db, dbx) with their own Platform Key, thereby defeating the whole purpose of UEFI Secure Boot. Only you should be able to replace the Platform Key, so only you should have access to the \texttt{noPK.auth} file. Therefore keep the \texttt{noPK.auth} file in a secret, safe place where only you have access to.
\end{quote}

@@

“You’re a bastard,” Techno said playfully, even as the voices screamed, run, run, run. He took Philza’s offered hand and pulled himself up beside the man that he was sure could have cut him in two, no matter how dulled the sword’s edge was. As Philza patiently moved Techno through all the things he’d done wrong (small things like foot placement and his hilt grip being an inch off), Techno found it equal parts amusing and frightening that despite his eons of bloody fighting, it took only a few minutes of sparring for Philza to find flaws in his technique. But then again, Techno’s technique wasn’t particularly polished; it took only one brutal swing to fell most people. Something told him that Philza would be harder to kill than that.

They conquered nations, he and his golden-haired friend. They were bathed in glory, twin gods shining in the middle of a bloody fields. But as their empire grew, so did their enemies. They came in droves, day after day, and before long Techno had forgotten what peace tasted like. The days were long and the nights were longer; every flicker of movement was a spy in the shadows, every ally was a potential traitor, every word was a declaration of war. Their home had become a target for a thousand armies.

Through it all, his one constant was Philza—until he wasn’t. Technoblade simply looked up one day from a map detailing enemy lines and realized he’d been talking to empty air. He had no idea how long he’d been alone, sitting in a dusty library with stale tea untouched in the corner. He had no idea if Philza ever said he was leaving, or if he simply went as he arrived suddenly, swiftly, like a snowstorm.

Afterwards, there was hardly any point in maintaining the empire. The voices were getting bored, anyway. They wanted more. A fresh fight, more stories. So Techno took his sword and his shield, and abandoned ship. He’d done it a million times before, but the thought of a chess board lying unused in a crumbling castle made him feeling something close to regret.

Technoblade wandered the world, trying to appease the voices. Neither of them were ever satisfied. No matter how much chaos he dealt, there was always more work to be done. So he worked. He had no idea for how long. All he remembered from that bloody time was a sense of unfulfillment, like a story had been left unfinished halfway through. Years. Decades. Maybe more. It hardly mattered.

In the end, he knew, it would all be the same. The world would end, and he would remain—always fighting, always alone. He’d seen it in his dreams, in the visions that plagued him. The world would end, and he would remain.

@@

\needspace{4\baselineskip}
\begin{question}
What is the main reason for Technoblade to abandon his empire and wander the world?
\begin{choices}
  \item He was bored with the empire and wanted to find new challenges.
  \item He was betrayed by his allies and was forced to leave the empire.
  \item He was haunted by the voices in his head and was unable to find peace.
  \item He was tired of fighting and wanted
\end{choices}
\end{question}

>>>>

The only way to prevent anyone with physical access from disabling Secure Boot is to protect the firmware settings with a password. Most UEFI firmwares provide such a feature, usually listed under the ``Security'' section in the firmware settings.

@@

\begin{choices}
\item Recent iterations of Xiaomi laptops give users access to the configuration of Secure Boot within the firmware only if the administrator password remains active after setting up. Users can possibly set the password in the ``Security'' section in the firmware settings.

@@

  \textbf{DO NOT} copy the \texttt{noPK.auth} file to the EFI system partition (ESP) of your PC! If you do this, and someone e.g. steals your PC, this person can delete the personal Platform Key in the UEFI Secure Boot firmware again, turn on ``Setup Mode'' on your PC again and replace your Secure Boot Keys (PK, KEK, db, dbx) with their own Platform Key, thereby defeating the whole purpose of UEFI Secure Boot. Only you should be able to replace the Platform Key, so only you should have access to the \texttt{noPK.auth} file. Therefore keep the \texttt{noPK.auth} file in a secret, safe place where only you have access to.
\end{quote}

@@

``You're a bastard,'' Techno said playfully, even as the voices screamed, ``Run, run, run.'' He took Philza's offered hand and pulled himself up beside the man that he was sure could have cut him in two, no matter how dulled the sword's edge was. As Philza patiently moved Techno through all the things he'd done wrong—small things like foot placement and his hilt grip being an inch off—Techno found it equal parts amusing and frightening that despite his eons of bloody fighting, it took only a few minutes of sparring for Philza to find flaws in his technique. But then again, Techno's technique wasn't particularly polished; it took only one brutal swing to fell most people. Something told him that Philza would be harder to kill than that.

They conquered nations, he and his golden-haired friend. They were bathed in glory, twin gods shining in the middle of bloody fields. But as their empire grew, so did their enemies. They came in droves, day after day, and before long Techno had forgotten what peace tasted like. The days were long and the nights were longer; every flicker of movement was a spy in the shadows, every ally was a potential traitor, every word was a declaration of war. Their home had become a target for a thousand armies.

Through it all, his one constant was Philza—until he wasn't. Technoblade simply looked up one day from a map detailing enemy lines and realized he'd been talking to empty air. He had no idea how long he'd been alone, sitting in a dusty library with stale tea untouched in the corner. He had no idea if Philza ever said he was leaving, or if he simply went as he arrived—suddenly, swiftly, like a snowstorm.

Afterwards, there was hardly any point in maintaining the empire. The voices were getting bored, anyway. They wanted more. A fresh fight, more stories. So Techno took his sword and his shield, and abandoned ship. He'd done it a million times before, but the thought of a chessboard lying unused in a crumbling castle made him feel something close to regret.

Technoblade wandered the world, trying to appease the voices. Neither of them was ever satisfied. No matter how much chaos he dealt, there was always more work to be done. So he worked. He had no idea for how long. All he remembered from that bloody time was a sense of unfulfillment, like a story had been left unfinished halfway through. Years. Decades. Maybe more. It hardly mattered.

In the end, he knew, it would all be the same. The world would end, and he would remain—always fighting, always alone. He'd seen it in his dreams, in the visions that plagued him. The world would end, and he would remain.

@@

\needspace{4\baselineskip}
\begin{question}
What is the main reason for Technoblade to abandon his empire and wander the world?
\begin{choices}
  \item He was bored with the empire and wanted to find new challenges.
  \item He was betrayed by his allies and was forced to leave the empire.
  \item He was haunted by the voices in his head and was unable to find peace.
  \item He was tired of fighting and wanted to find a way to end the world.
\end{choices}
\end{question}
